Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study

### 2022-03-14 paper.tex
update

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{floatrow}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

\newcommand{\MyDiamond}[1][fill=black]{
\begin{tikzpicture}[x=1.2ex,y=1.2ex,line width=.1ex,line join=round, yshift=0.0ex]\
\draw  [#1]  (0,.5) -- (.5,1) -- (1,.5) -- (.5,0);
\end{tikzpicture}
}

\newcommand{\MyPlus}[1][fill=black]
{
\begin{tikzpicture}[x=1.5ex,y=1.5ex,line width=0.5ex]
\draw[#1] (0,.5) -- (1,.5);
\draw[#1] (.5,0) -- (.5,1);
\end{tikzpicture}
}

\newcommand{\MyCross}[1][fill=black]
{
\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.5ex]
\draw[#1] (0,0) -- (1,1);
\draw[#1] (0,1) -- (1,0);
\end{tikzpicture}
}

\newcommand{\MyTriangle}[1][fill=black]
{
\begin{tikzpicture}[x=1.ex,y=1.ex,line width=0.2ex]
\draw[#1] (0,1) -- (1,1);
\draw[#1] (1,1) -- (.5,0);
\draw[#1] (.5,0) -- (0,1);
\fill[#1] (0,1) -- (1,1) -- (.5,0) -- cycle;
\end{tikzpicture}
}

\newcommand{\MySolidLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw[#1] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDashedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dashed] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDashedDottedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dash dot] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\newcommand{\MyDottedLine}[1][fill=black]
{
\begin{tikzpicture}[x=2.ex,y=1.ex,line width=0.5ex]
\draw [#1,dotted] (0,.5) -- (2.5,.5);
\end{tikzpicture}
}

\definecolor{Gray}{gray}{0.85}

\begin{document}
\title{The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study}

\author[0000-0002-1868-0660]{Po-Hsun Tseng}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}

\author[0000-0003-3269-4660]{H.-Y. Karen Yang}
\affiliation{Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
\affiliation{Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan}
\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}

\author[0000-0002-1249-279X]{Hsi-Yu Schive}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan}

\author{Chun-Yen Chen}
\affiliation{Institute of physics, National Taiwan University, Taipei 10617, Taiwan}

\author[0000-0003-2654-8763]{Tzihong Chiueh}
\affiliation{Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Department of Physics, National Taiwan University, Taipei 10617, Taiwan}
\affiliation{Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan}

\correspondingauthor{Po-Hsun Tseng}
\email{zengbs@gmail.com}

\keywords{\textit{Fermi} bubbles, eROSITA bubbles, cosmic rays}

\begin{abstract}
The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ on either side of the Galactic center (GC).\
The recent discovery of giant eROSITA bubbles also shows a symmetrically enhanced X-ray\
emission from the shells around the eROSITA bubbles.\
To this end, previous simulation-based works based on active galactic nucleus (AGN) jets model\
assumed that the jets are vertical to the Galactic disk;\
however, there is a lack of preferred orientation of jets with respect to the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is a substantial\
component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
an oblique AGN jets model. We find that\
(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
the bipolar jets are at an angle $45^{\circ}$ with respect to\
the rotation axis of the Galatic plane (disc normal hereafter).\
(2) The edge of the eROSITA bubbles is a forward shock,\
originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
and significantly stretched by the stratified atmosphere afterwards.\
(3) Followed by the forward shock is a\
hot ($\sim2$ keV), turbulent, and pressure-balanced plasma,\
which we interpret as the \textit{Fermi} bubbles.\
Inside the simulated \textit{Fermi} bubbles,\
there are two additional innermost bubbles we have not detected yet.\
The innermost bubbles are essentially a reverse shock permanently associated with the disk.\
(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
CRe power-law index is found to be 2.4.\
The broad agreement between the simulations and observations\
, either from the point of view of their morphology or multiwavelength features,\
has thus released a caveat:\
the jets shall be vertical to the disc normal.
\end{abstract}

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.

The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
of 1--100 GeV and has an almost spatially uniform hard\
spectrum, sharp edges and an approximately flat brightness distribution.\

@@

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (Schive et al. \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
  and directly evolve the CR energy density $e_{\text{cr}}$\
  as a function of $\mathbf{r}$ and $t$.\
  The CRs are advected with the thermal gas, and in return the velocities of gas\
  can react to the gradients of the CR pressure via the source term\
  containing spatial divergence of fluid velocities.

@@

  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

%  The density profile of \Cref{disc-atm-sys} is shown in \Cref{fig__initial-density-profile}\
%  and compared to the observed result \citep{Miller_2013} beyond 1 kpc.\
%
%  Note that there is an difficulty in disentangling the contribution\
%  of the Local Bubble, a supernova remnant in which the Solar System is embedded \citep{Snowden1990},\
%  and the contribution from solar wind charge-exchange processes, which produce soft\
%  X-ray emission throughout the Solar System. As a result, the density profile of the Galactic halo remains unclear\
%  \citep{BlandHawthorn2016}.

@@

\begin{table*}[t]
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity                   & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disc                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                           &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

% In addition to the gravitational interaction, we ignore other interactions between stars and gases.
% We also ignore the self-gravity of the ISM disc and of the atmosphere.
% We ignore the centrifugal force of Milky Way rotation acting on the bubbles.
%

@@

 \Cref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middle), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction.

 The fiducial run (a1-a3) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
 based on X-ray emissions.

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 the smooth region (purple band in \Cref{fig__profile}) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

 Followed by the forward shock is a turbulent and hot plasma\
 in pressure balance with the external medium.\
 As shown in the temperature or density slices of the fiducial run,\
 the full extent of the turbulent plasma is 9 kpc, fairly close to\
 that of the observed \textit{Fermi} bubbles \citep{Su2010}.
 Also, the temperature of the plasma is as high as 2 keV,\
 comparable to few keV inside the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
 The general agreement of extent and temperature\
 suggests that the \textit{Fermi} bubbles\
 is essentially a turbulence rather than a smooth shock \citep{Zhang2020}.

 The most interesting finding is that there are innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\

 Moreover, the close-up view (right column in \Cref{fig__profile})\
 of profiles and slices (\Cref{fig__innerbubbles})\
 demonstrates that the pressure rises dramatically outward across\
 the edge of the innermost bubbles,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a dense shell.

@@

 To explore how the disk affects the formation of the Galactic bubbles,\
 we compare the fiducial run (panels a1-a3 in \Cref{fig__jetI5+ismSeed3-45deg})\
 with the case adopting the smooth disc\
 (panels b1-b3; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
 The results show that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (panels c1-c3) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg.png}
    \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (a1-a3)\
             and the smooth disc (b1-b3) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (c1-c3) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, the two rightmost columns reveal that the development of the innermost bubbles\
             (a1)\
             is always associated with the disc, without the disc,\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
             }
    \label{fig__jetI5+ismSeed3-45deg}
  \end{figure}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__profile.png}
    \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in \Cref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
             are an expanding reverse shock.
     }
    \label{fig__profile}
  \end{figure}

>>>>

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{mnras}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{orcidlink}
\usepackage{url}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage[flushleft]{threeparttable}
\usepackage{caption}
\usepackage{subcaption}

\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
%
%
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[]{Can the symmetric \textit{Fermi} and eROSITA bubbles be produced by tilted jets: a proof-of-concept study}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[P. H. Tseng et al.]{\large
Po-Hsun Tseng$^{1}$%
\thanks{\href{mailto:zengbs@gmail.com}{zengbs@gmail.com}}%
\orcidlink{https://orcid.org/0000-0002-1868-0660}%
\quad H.-Y. Karen Yang$^{2,3,4,5}$%
\thanks{\href{mailto:hyang@phys.nthu.edu.tw}{hyang@phys.nthu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-3269-4660}%
\quad Hsi-Yu Schive$^{1,5,6,7}$%
\thanks{\href{mailto:hyschive@phys.ntu.edu.tw}{hyschive@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0002-1249-279X}%
\quad Chun-Yen Chen$^{8}, $
\quad Tzihong Chiueh$^{1,5,6}$%
\thanks{\href{mailto:chiuehth@phys.ntu.edu.tw}{chiuehth@phys.ntu.edu.tw}}%
\orcidlink{https://orcid.org/0000-0003-2654-8763}%
\\\\
$^{1}$Institute of Astrophysics, National Taiwan University, Taipei 10617, Taiwan\\
$^{2}$Institute of Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{3}$Department of Physics, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{4}$Center for Informatics and Computation in Astronomy, National Tsing Hua University, Hsinchu 30013, Taiwan\\
$^{5}$Physics Division, National Center for Theoretical Sciences, Taipei 10617, Taiwan\\
$^{6}$Department of Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{7}$Center for Theoretical Physics, National Taiwan University, Taipei 10617, Taiwan\\
$^{8}$Institute of physics, National Taiwan University, Taipei 10617, Taiwan\\
}

% These dates will be filled out by the publisher
\date{\today}

% Enter the current year, for the copyright statements etc.
\pubyear{2022}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
The \textit{Fermi Gamma-Ray Space Telescope} reveals two large bubbles in the Galaxy,\
which extend nearly symmetrically $\sim50^{\circ}$ above and below the Galactic center (GC).\
The recent discovery of giant eROSITA bubbles also shows such a symmetry about the GC, suggesting that they may originate from a single GC activity.\
Previous simulations of bubble formation that invoke active galactic nucleus (AGN) jets\
have assumed that the jets are vertical to the Galactic plane;\
however, in general there does not need to be a correlation between the jet orientation and the rotational axis of the Galactic disk.\
Using three-dimensional (3D) special relativistic hydrodynamic (SRHD) simulations that\
include cosmic rays (CRs) and thermal gas, we show that a thin interstellar medium (ISM) disk is an essential\
component for the symmetric \textit{Fermi} and eROSITA bubbles (collectively, Galactic bubbles).\
We also produce simulated gamma-ray and\
microwave spectra from the inverse Compton (IC) scattering and synchrotron,\
and compare them with the observed counterparts in order to verify\
an oblique AGN jets model. We find that\
(1) The simulated Galactic bubbles are nearly symmetric about the GC albeit\
the bipolar jets are at an angle $45^{\circ}$ with respect to\
the rotation axis of the Galatic plane (disc normal hereafter).\
(2) The edge of the eROSITA bubbles is a forward shock,\
originally driven by oblique bipolar jets emanating from the GC 12.39 million years ago,\
and significantly stretched by the stratified atmosphere afterwards.\
(3) Followed by the forward shock is a tangling contact discontinuity,\
which we interpret as the edge of the \textit{Fermi} bubbles\
composed of turbulent and high-temperature ($\sim2$ keV)\
plasma in pressure balance with the external medium.
(4) According to the microwave and leptonic gamma-ray spectra, the best-fitting\
CRe power-law index is found to be 2.4.\
The broad agreement between simulated and observed multiwavelength features\
has thus released a caveat:\
the jets shall be vertical to the disc normal.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
editorials, notices -- miscellaneous
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

% The MNRAS class isn't designed to include a table of contents, but for this document one is useful.
% I therefore have to do some kludging to make it work without masses of blank space.
\begingroup
\let\clearpage\relax
%\tableofcontents
\endgroup
\newpage

\section{Introduction}
The detection of the \textit{Fermi} bubbles \citep{Su2012,Ackermann2014,Narayanan2017},\
two large bubbles symmetrically extending about 50 degrees above and below the Galactic plane,
is one of the great discoveries made with \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
The gamma-ray emission of the \textit{Fermi} bubbles is observed in the energy range\
of 1--100 GeV and has an almost spatially uniform hard\
spectrum, sharp edges and an approximately flat brightness distribution.\

@@

\section{Methodology}
\label{Methodology}
  We used the GPU-accelerated special relativistic\
  hydrodynamics AMR code (\textsc{gamer-sr}) developed at the\
  National Taiwan University\
  (\citeauthor{gamer-1} \citeyear{gamer-1}, \citeyear{gamer-2}; \citeauthor{tseng2021} \citeyear{tseng2021})\
  to carry out the simulations of the Galactic bubbles by CR and relativistic fluid injections from the GC.

@@

  In this approach, we treat CRs as a single species without distinction between electrons and protons,\
  and directly evolve the CR energy density $e_{\text{cr}}$\
  as a function of \textbf{r} and $t$.\
  The CRs are advected with the thermal gas, and in return the velocities of gas\
  can react to the gradients of the CR pressure via the source term\
  containing spatial divergence of fluid velocities.

@@

  The density profile of Eq. \ref{disc-atm-sys} is shown in Fig. \ref{fig__initial-density-profile}.\
  Beyond the core radius ($\sim 2 \text{ kpc}$) the gaseous density decreases rapidly as a power-law.

@@

\begin{table*}
\raggedright
\caption{Parameters of the disc, atmosphere, and gravitational potential in the simulations.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                    & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge   & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge  & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                &                                      &                                \\
$v_{\text{halo}}$                     & Characteristic velocity        & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                    & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere      & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disc }                &                                &                                      &                                \\
$z_{0}$                               & Scale height of disc           & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disc            & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disc      & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disc }                    &                                &                                      &                                \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number             & 375.0                                & \citep{peak-ism-density}       \\
$\mu$                                 & Mean of scalar field           & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field     & 5.0                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual molecular cloud $\sim 100$ pc.
      \item  $\ddag$ In numerical simulations of turbulence,\
             \citet{Federrath2010} find $\sigma\sim 3.6$ and 35 for solenoidal (divergence-free)\
             and compressive (curl-free) driving force,\
             respectively, so that our adopted value of 5 is closer to their solenoidal result.
    \end{tablenotes}
\end{table*}

%

@@

 Fig. \ref{fig__jetI5+ismSeed3-45deg} shows\
 the slices of pressure (top), temperature (middle), number density (bottom)\
 at the end of simulation $t=12.39$ Myr.\
 The slices pass through the bipolar jet source injecting along $z=-y$ direction.

 The fiducial run (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020}\
 for modeling the eROSITA bubbles\
 based on X-ray emissions.

 The temperature profile (left middle panel in Fig. \ref{fig__profile}) along the positive z-axis in\
 Fig. \ref{fig__jetI5+ismSeed3-45deg} indicates that\
 the temperature of the smooth region (purple band in Fig. \ref{fig__profile}) emitting X-ray\
 is around 0.3-0.5 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

 Followed by the forward shock is a turbulent and hot plasma.\
 As shown in the temperature or density slices of the fiducial run,\
 the full extent of the turbulent plasma is approximately agree with\
 that of the observed \textit{Fermi} bubbles \citep{Su2010}.
 Also, the temperature of the plasma is as high as 2 keV,\
 comparable to few keV inside the \textit{Fermi} bubbles\
 obtained by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
 We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
 suggesting the outer edge of the \textit{Fermi} bubbles\
 is a turbulence rather than a smooth shock \citep{Zhang2020}.

 The most interesting finding is that there are innermost bubbles\
 (dashed box in the top panel of Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 extending out from the GC on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$--$10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\

 Moreover, the close-up view (right column in Fig. \ref{fig__profile}) of profiles\
 and slices (Fig. \ref{fig__innerbubbles})\
 demonstrate that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
 indicating that the innermost bubbles are an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a dense shell.

@@

 Fig. \ref{fig__jetI5+ismSeed3-45deg} shows the slices of various gas properties at $t=12.39$ Myr,\
 including pressure (top), temperature (middle),\
 density (bottom) with the same jet source as the fiducial run\
 but in different Galactic environments.

 We compare the clumpy disk (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
 with the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}),\
 specified by the initial density profile shown in Fig. \ref{fig__initial-density-profile},\
 in a stratified atmosphere.\
 The results show that the initial density distribution of\
 the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
 reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

 \begin{figure}%
      \captionsetup[subfigure]{labelformat=simple}
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-a}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-a}%
      \end{subfigure}%
      \hspace{10pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-b}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-b}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-c}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-c}%
      \end{subfigure}%
      \hspace{-2pt}%
      \begin{subfigure}[b]{0.2\linewidth}%
         \includegraphics[height=10cm]{figures/fig__jetI5+ismSeed3-45deg-d}%
         \caption{}%
         \label{fig__jetI5+ismSeed3-45deg-d}%
     \end{subfigure}%
      \caption{
             The slices of pressure (top), temperature (middle), and number density (bottom)\
             at the end of simulation $t=12.39$ Myr.\
             The slices pass through a bipolar jet source injecting along $z=-y$ direction\
             for a duration $t=0$--$1.2$ Myr.\
             Comparison between the clumpy (Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             and the smooth disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-b}) in a stratified atmosphere\
             shows that the initial density distribution of the dense disc has an insignificant effect\
             on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
             in an uniform atmosphere (Fig. \ref{fig__jetI5+ismSeed3-45deg-c}) is spherical-shape,\
             suggesting the stratification facilitates the outermost bubbles elongation significantly.\
             Also, Fig. \ref{fig__jetI5+ismSeed3-45deg-c} and \ref{fig__jetI5+ismSeed3-45deg-d}\
             reveal that the development of the innermost bubbles\
             is always associated with the disc, without the disc (Fig. \ref{fig__jetI5+ismSeed3-45deg-d}),\
             the outermost bubbles and the turbulent plasma will be oblique,
             indicating the dense disc is crucial for\
             the symmetry of the Galactic bubbles and for the innermost bubbles formation.
      }
      \label{fig__jetI5+ismSeed3-45deg}
 \end{figure}%

 \begin{figure}%
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-1.png}%
         \label{fig__profile-1}%
      \end{subfigure}%
      \hspace{4pt}
      \begin{subfigure}[t]{0.5\linewidth}%
         \includegraphics[height=8cm]{figures/fig__profile-2.png}%
         \label{fig__profile-2}%
      \end{subfigure}%
      \caption{
             Left: the profiles of pressure (top), temperature (middle),\
             and number density (bottom)\
             along the positive z-axis in Fig. \ref{fig__jetI5+ismSeed3-45deg}.
             Right: the close-up view of the profiles in the yellow band.\
             The sharp pressure jump at $z=3.62$ kpc\
             indicates that the innermost bubbles\
             (dashed box in the top panel in Fig. \ref{fig__jetI5+ismSeed3-45deg-a})\
             are an expanding reverse shock.
      }%
      \label{fig__profile}%
 \end{figure}%
